---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EGHS

<!-- badges: start -->
<!-- badges: end -->

The goal of EGHS is to provide two working Harvest Control Rules to illustrate the use of the aMSE software.

Harvest Control Rules differ from harvest strategies in that they literally take the stock status, as derived from whatever analysis is done to the data from the fishery (in the case of abalone this relates to standardizing the CPUE) and in their turn, derive a future catch level. A harvest strategy would include descriptions of what data to use, what analysis to apply, and what harvest control rule to apply. The current Tasmanian harvest strategy differs from the two harvest control rules (hcr) included in **EGHS**, and continues to be developed. Hence it is not suitable for inclusion in the examples within _aMSEGuide_.

Two harvest control rules are provided:

* Constant Catch _consthcr_, which, as its name suggests simply applies a constant aspirational catch to each sau across all projections. This is the simplest hcr.
* Adaptive reference period, _mcdahcr_, which reflects the original HCR used in Tasmania (Bradshaw, 2018), where the reference period used to generate CPUE targets increases as the years of projection increase. This is a much more complex empirical harvest strategy, especially when including the three meta-rules that are used to tune the outcome of the hcr to more closely match the objectives of the harvest strategy (HS).

## Installation

You can install the development version of EGHS from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("haddonm/EGHS")
```

## Example



```{r example}
library(EGHS)
?EGHS


```
